Function to find association b/w n significant eigen genes with Diagnosis, Diagnosis.Gender, ApoE

### 2017-09-20 code/Rmd/networkAssociationTest.Rmd
Minor bug fix

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn10306449';
activityName = 'Network associaiton statistics';

@@

### Data download
```{r download.data, cache=FALSE, include=FALSE}
# Download data
MODULES = synTableQuery('SELECT * FROM syn10338156')@values
all.used.ids = c('syn10338156')

@@

  getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```
Top 5 modules any method
```{r Dx.gender.2, fig.height=12, fig.width=12}
# Top 5 any method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(25, total.eff.sz) %>%
    dplyr::top_n(25, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)
  print(summary(factor(imp.mods$method)))

  getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```

@@

### Store results in synapse
```{r syn.store, cache = FALSE, include=FALSE}
CODE = Folder('Network Association Tests', parentId = "syn10306449")
CODE = synStore(CODE)

>>>>

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = FALSE)
```

```{r synapse.parameters, include=FALSE}
parentId = 'syn10306449';
activityName = 'Network associaiton statistics';

@@

### Data download
```{r download.data, include=FALSE}
# Download data
MODULES = synTableQuery('SELECT * FROM syn10338156')@values
all.used.ids = c('syn10338156')

@@

  print(dim(imp.mods)[1])
  print(br)

  if(dim(imp.mods)[1] != 0 ){
    getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
  }
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
# draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```
Top 5 modules any method
```{r Dx.gender.2, fig.height=12, fig.width=12}
# Top 5 any method
h = lapply(unique(Dx.gender$brainRegion), function(br, Dx, MOD.MEMBERS, MODULE.OVRLP){
  imp.mods = Dx %>%
    dplyr::group_by(brainRegion) %>%
    dplyr::filter(total.fdr <= 0.05) %>%
    dplyr::top_n(25, total.eff.sz) %>%
    dplyr::top_n(25, pc1.eff.sz) %>%
    dplyr::filter(brainRegion == br)
  print(dim(imp.mods)[1])
  print(br)

  if(dim(imp.mods)[1] != 0 ){
    print(summary(factor(imp.mods$method)))
    getOverlapPlots(imp.mods, MOD.MEMBERS, MODULE.OVRLP)
  }
}, Dx.gender, MOD.MEMBERS, MODULE.OVRLP)
draw(h[[1]], heatmap_legend_side='left')
# draw(h[[2]], heatmap_legend_side='left')
draw(h[[3]], heatmap_legend_side='left')
draw(h[[4]], heatmap_legend_side='left')
draw(h[[5]], heatmap_legend_side='left')
draw(h[[6]], heatmap_legend_side='left')
draw(h[[7]], heatmap_legend_side='left')
```

@@

### Store results in synapse
```{r syn.store, include=FALSE}
CODE = Folder('Network Association Tests', parentId = "syn10306449")
CODE = synStore(CODE)
